Tracing the Meta-Level: PyPy's Tracing JIT Compiler

### 2009-04-08 talk/icooolps2009/paper.tex
fix supposed holgerism

Such a history is called a \emph{trace}: it is a sequential list of
operations, together with their actual operands and results.  By examining the
trace, it is possible to produce highly efficient machine code by generating
only the operations needed.  Being sequential, the trace represents only one
of the many possible paths through the code. To ensure correctness, the trace
contains a \emph{guard} at every possible point where the path could have
followed another direction, for example conditions or indirect/virtual
calls.  When generating the machine code, every guard is turned into a quick check
to guarantee that the path we are executing is still valid.  If a guard fails,
we immediately quit the machine code and continue the execution by falling
back to interpretation.

>>>>

Such a history is called a \emph{trace}: it is a sequential list of
operations, together with their actual operands and results.  By examining the
trace, it is possible to produce highly efficient machine code by generating
only the operations needed.  Being sequential, the trace represents only one
of the many possible paths through the code. To ensure correctness, the trace
contains a \emph{guard} at every possible point where the path could have
followed another direction, for example conditions and indirect or virtual
calls.  When generating the machine code, every guard is turned into a quick check
to guarantee that the path we are executing is still valid.  If a guard fails,
we immediately quit the machine code and continue the execution by falling
back to interpretation.
